Searching for long-period transiting planets in the \kepler\ light curves using supervised classification

### 2015-04-09 document/ms.tex
parameter inference figure
more samples and words

This search results in 596 candidate transits in the light curves of these
3500 stars.
The vast majority of these candidates are misclassified false positives and
many of them are caused by astrophysical sources.
To weed out known astrophysical sources, we cross-match this list against
known eclipsing binary stars \citep{Matijevic:2012} and stars with substantial
variability \citep{McQuillan:2014}.
Removing these signals results in 273 candidates.

\paragraph{A discovery}

@@

\section{Parameter estimation}\sectlabel{params}

Even though only one transit is observed, it is still possible to estimate the
orbital period of these planet candidates using independent constraints on the
stellar properties.
This technique is similar in spirit to the ``photoeccentric effect''
\citep{Dawson:2012} and ``asterodensity profiling'' \citep{Kipping:2012}.
The fundamental principle is that, the transit duration is a measurement of
the instantaneous velocity of the planetary motion and this yields a
constraint on the orbital period when combining this with a measurement of the
stellar density and a prior on the eccentricity of the orbit.

>>>>

This search results in 596 candidate transits in the light curves of these
3500 stars.
The vast majority of these candidates are misclassified false positives and
many of them are caused by astrophysical sources.
To weed out known astrophysical sources, we cross-match this list against
known eclipsing binary stars \citep{Matijevic:2012} and stars with substantial
variability \citep{McQuillan:2014}.
Removing these signals results in 273 candidates.
Of these candidates only one (KIC 10602068) is a convincing transit and the
others all appear to be caused by systematic effects, instrumental or
astrophysical.
\Fig{candidates} shows some representative candidate signals from this final
list.

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/candidates.pdf}
\end{center}
\caption{%
\figlabel{candidates}}
\end{figure}

\section{KIC 10602068: A discovery}\sectlabel{params}

In the 3500 light curves we searched for this \paper, we discovered one
convincing single transit signal at $830.80921\pm0.00015$~KBJD in the light
curve of the 14.9~Kep-mag G-dwarf KIC 10602068.
Despite the fact that this is a very large signal, its discovery has never
been reported.
Given the estimate of $\sim 60$ detectable single transits in the full
\kepler\ archival dataset, we expect about one discovery in 3500 light curves.

Even though only one transit is observed, it is still possible to place
constraints on the physical properties---even the orbital period---of this
transiting body.
This technique is similar in spirit to the ``photoeccentric effect''
\citep{Dawson:2012} and ``asterodensity profiling'' \citep{Kipping:2012}.
The fundamental principle is that the transit duration is a measurement of
the instantaneous velocity of the planetary motion and this yields a
constraint on the orbital period when combining this with a measurement of the
stellar density and a prior on the eccentricity of the orbit.

The \citet{Huber:2014} parameters for this star place it as a G-dwarf with a
radius of $\sim 0.9\,R_\odot$ $2.02 \pm 0.25\,R_\mathrm{J}$.
